|

### 2023-04-10 paper/01-introduction.Rmd
First Draft of intro.

## Previous Pass-Rush Measure in academic literaure 
@AlamarGould2008: Abstract: Protecting the quarterback is an integral part of the passing game in the National Football league, yet the relationship between the abilities of an individual lineman and the effectiveness of a passing game remains unexplored. One of the principal reasons for this lack of study is the absence of publicly available data that is needed in order to track the performance of a specific lineman. In order to create the relevant data, the first 3 games of the 2007 NFL season for seven different teams were charted. The performance of each lineman was recorded on every pass play, as well as the amount of undisturbed time the quarterback was given (time in the pocket) to make a throw. These data were used in a series of regressions to determine how likely a lineman was to successfully hold his block in relation to the time it took for the quarterback to throw the ball, for each lineman in the sample. These data were also used to estimate the correlation between successful blocking and completion rate. The results of these regressions were then used to simulate the effects that different linemen have on the passing game. The trade in the offseason between the New York Jets and Washington Redskins which sent left guard Pete Kendall to Washington was examined. The analysis finds that the Jets lost approximately 3 percentage points on their completion rate due to the trade.

@AlamarGoldner2011: They talk about how there is no data available to measure offensive line performance.  1259 plays, 20 teams, 2010 season.  Success of each offensive lineman was evaluated using the best judgement of the observer.   Collected time in pocket.  They collected a bunch of binary variables and did this all by HAND!  Estimate a survival model for each position on the offensive line.  They don't rank individuals, but rather positions on a team.  They then use the predicted probability as a covariate in a model to predict completion.

Pass Rush productivity 
Time in pocket
Pass Rush win rate

hurries hits and sacks are "pressures"

Limitations

Sacks, hits, hurries, pressures

Officially tracked by the NFL since 1982, the most well known statistic for evaluating defensive linemen on pass rushing plays is the sack, which occurs when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass.

Sack definition:

https://www.pro-football-reference.com/about/advanced_stats.htm

Pressures: QB pressures (hurries + knockdowns + sack plays). Note that "sack plays" in this instance include both sacks and assists.

Hurried: Times QBs were hurried - defined as a situation when the QB is forced to throw the ball earlier than intended or is chased around/out of the pocket as the result of defensive pressure

Hit: Times QBs were hit - occurs when the QB hits the ground after a throw, not marked on a sack play

PFF's Pass-Rush Productivity (PRP)

https://www.pff.com/news/pro-signature-stats-spotlight-defensive-line

More recently metrics such as Time In Pocket (TIP) and Pass Rush Win Rate (PRWR) have also been proposed and are substantial improvements over the less sophisticated counting statistics.

Pocket Time: Number of seconds the quarterback was in the pocket between the snap of the ball and a pass or the collapse of the pocket

@Burke2018Created
@AlamarGoldner2013: They talk about how there is no data available to measure offensive line performance.  1259 plays, 20 teams, 2010 season.  Success of each offensive lineman was evaluated using the best judgement of the observer.   Collected time in pocket.  They collected a bunch of binary variables and did this all by HAND!  Estimate a survival model for each position on the offensive line.  They don't rank individuals, but rather positions on a team.  They then use the predicted probability as a covariate in a model to predict completion.

@AlamarGould2008

https://www.espn.com/nfl/story/_/id/24892208

2.5 seconds, arbitrary

While PRWR is certainly a step in the right direction, it takes continuous data and converts it to a binary win/loss, which is generally not recommended in statistical analysis

## Contributions of STRAIN

STRAIN is the best etc.

The remainder of this paper is outlined as follows.

Section \ref{sec:data}

Section \ref{sec:methods}

Section \ref{sec:results}

Section \ref{sec:discussion}

>>>>

## Previous Pass-Rush Measure in academic literaure
The academic literature on the performance of linemen, either offensive or defensive in football is scant. @AlamarGould2008 studied the the relationship between pass completion rate and performance of offensive linemen in terms of how successful they were at blocking.  The data for this study was collecting essentially by hand by watching and charting the performance of each lineman on a play.  This was done using games from the beginning 2007 season for seven teams and their first three games each.  The authors note that there is not much research on linemen saying "One of the principal reasons for this lack of study is the absence of publicly available data that is needed in order to track the performance of a specific lineman."

Later, @AlamarGoldner2011 again studied offensive linemen performance.  They analyzed 20 teams during the 2010 season for a total of 1,259 plays.  They don't estimate the performance of an individual lineman, but rather positions on a team (e.g. Chicago Bears' left tackle, Pittsburgh Steelers' center, etc.).  They then go on to use a survival analysis model to estimate time in pocket.  The average probability of success from the survival model is then used as a covariate in a model to estimate the probability of competing a pass, and they show that there is a significant relationship between these two probabilities.

## Contributions of STRAIN
All the aforementioned methods suffered from not having the data that was actually necessary to develop a meaningful metric for linemen in football, either offensive or defensive.  Now though, thanks to the 2023 Big Data Bowl, we have a publicly available tracking data not only for the linemen, but for every player on the field!  With this data performance of offensive and defensive linemen can be meaningfully assessed, though we focus solely on the performance of defensive linemen here.  This manuscript presents a metric we refer to as STRAIN based on a concept of the same name from materials science.  STRAIN gives a continuous measure of pressure for each of the defensive linemen over the course of an entire play allowing for the measurement of the level of success of the pass rush even on plays that don't result in an easily observed outcome like a sack, hit, or hurry.  We view this as a major step forward in the accurate evaluation of defensive linemen performance.  Further, we note than while we focus exclusively on defensive linemen here, the proposed metric STRAIN is relatively easily extended to the evaluation of offensive linemen performance.

The remainder of this paper is outlined as follows. Section \ref{sec:data} describes the data set from the 2023 Big Data Bowl.  Section \ref{sec:methods} introduces the formal definition of STRAIN.  Section \ref{sec:results} studies the performance of the proposed metric.  We end with Section \ref{sec:discussion} where we present a discussion of future directions for STRAIN.

<!-- : They talk about how there is no data available to measure offensive line performance.  1259 plays, 20 teams, 2010 season.  Success of each offensive lineman was evaluated using the best judgement of the observer.   Collected time in pocket.  They collected a bunch of binary variables and did this all by HAND!  Estimate a survival model for each position on the offensive line.  They don't rank individuals, but rather positions on a team.  They then use the predicted probability as a covariate in a model to predict completion.  -->

<!-- @AlamarGould2008: Abstract: Protecting the quarterback is an integral part of the passing game in the National Football league, yet the relationship between the abilities of an individual lineman and the effectiveness of a passing game remains unexplored. One of the principal reasons for this lack of study is the absence of publicly available data that is needed in order to track the performance of a specific lineman. In order to create the relevant data, the first 3 games of the 2007 NFL season for seven different teams were charted. The performance of each lineman was recorded on every pass play, as well as the amount of undisturbed time the quarterback was given (time in the pocket) to make a throw. These data were used in a series of regressions to determine how likely a lineman was to successfully hold his block in relation to the time it took for the quarterback to throw the ball, for each lineman in the sample. These data were also used to estimate the correlation between successful blocking and completion rate. The results of these regressions were then used to simulate the effects that different linemen have on the passing game. The trade in the offseason between the New York Jets and Washington Redskins which sent left guard Pete Kendall to Washington was examined. The analysis finds that the Jets lost approximately 3 percentage points on their completion rate due to the trade. -->

<!-- Is this interesting? https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2938948/ -->

<!-- Evaluating offensive line salray: https://sites.duke.edu/djepapers/files/2016/10/froelich-dje.pdf -->

<!-- Read this:  -->
<!-- https://www.researchgate.net/profile/Gita-Sukthankar/publication/220814393_A_Real-Time_Opponent_Modeling_System_for_Rush_Football/links/00b7d528a16b30fc12000000/A-Real-Time-Opponent-Modeling-System-for-Rush-Football.pdf -->

<!-- Pass Rush productivity  -->
<!-- Time in pocket -->
<!-- Pass Rush win rate -->

<!-- hurries hits and sacks are "pressures" -->

<!-- Limitations -->

<!-- Sacks, hits, hurries, pressures -->

<!-- Officially tracked by the NFL since 1982, the most well known statistic for evaluating defensive linemen on pass rushing plays is the sack, which occurs when a defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass. -->

<!-- Sack definition:  -->

<!-- https://www.pro-football-reference.com/about/advanced_stats.htm -->

<!-- Pressures: QB pressures (hurries + knockdowns + sack plays). Note that "sack plays" in this instance include both sacks and assists. -->

<!-- Hurried: Times QBs were hurried - defined as a situation when the QB is forced to throw the ball earlier than intended or is chased around/out of the pocket as the result of defensive pressure -->

<!-- Hit: Times QBs were hit - occurs when the QB hits the ground after a throw, not marked on a sack play -->

<!-- PFF's Pass-Rush Productivity (PRP) -->

<!-- https://www.pff.com/news/pro-signature-stats-spotlight-defensive-line -->

<!-- More recently metrics such as Time In Pocket (TIP) and Pass Rush Win Rate (PRWR) have also been proposed and are substantial improvements over the less sophisticated counting statistics.  -->

<!-- Pocket Time: Number of seconds the quarterback was in the pocket between the snap of the ball and a pass or the collapse of the pocket -->

<!-- @Burke2018Created -->
<!-- @AlamarGoldner2013: They talk about how there is no data available to measure offensive line performance.  1259 plays, 20 teams, 2010 season.  Success of each offensive lineman was evaluated using the best judgement of the observer.   Collected time in pocket.  They collected a bunch of binary variables and did this all by HAND!  Estimate a survival model for each position on the offensive line.  They don't rank individuals, but rather positions on a team.  They then use the predicted probability as a covariate in a model to predict completion.   -->

<!-- @AlamarGould2008 -->

<!-- https://www.espn.com/nfl/story/_/id/24892208 -->

<!-- 2.5 seconds, arbitrary -->

<!-- While PRWR is certainly a step in the right direction, it takes continuous data and converts it to a binary win/loss, which is generally not recommended in statistical analysis -->
